A Gentle Introduction and Application of Feature-Based Clustering with Psychological Time Series

### 2023-07-29 sections/07ClusterEvaluationInterpretation.Rmd
feedback lfb

  # Create the forest plot
  concept_plot_list[[concept]] <- forestplot::forestplot(labeltext = plot_matrix[, 1], 
             mean = as.numeric(plot_matrix[, 2]),
             lower = as.numeric(plot_matrix[, 3]),
             upper = as.numeric(plot_matrix[, 4]),
             xlab = "Difference",
             title = paste0("Forest plot for ", concept))
}

@@

  paste("$difference$ = ", diff,
        ", $t$(", df, ") = ", t,
        ", $p$ ", p , 
        ", $95%CI$ [", lwr,
        ", ", upr, "]",
        sep = "")
}
```

>>>>

  # Create the forest plot
  concept_plot_list[[concept]] <- forestplot::forestplot(labeltext = plot_matrix[, 1], 
             mean = as.numeric(plot_matrix[, 2]),
             lower = as.numeric(plot_matrix[, 3]),
             upper = as.numeric(plot_matrix[, 4]),
             xlab = "Difference")
}

@@

  paste("\\textit{difference} = ", diff,
        ", $t$(", df, ") = ", t,
        ", $p$ ", p , 
        ", \\textit{95\\%CI} [", lwr,
        ", ", upr, "]",
        sep = "")
}
```
